\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-30 paper.qmd
Added references for acknowledged works

These `R` packages were used for the work:. These `python` packages were used for the work:. The article was created with `R` packages `rticles`, `knitr`, and `rmarkdown`. The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

>>>>

These `R` packages were used for the work: `tidyverse` (@hadley2019), `png` (@simon2022), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `ggplot2` (@hadley2016), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work:. The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

### 2024-09-30 paper.tex
Added references for acknowledged works

These \texttt{R} packages were used for the work:. These \texttt{python}
packages were used for the work:. The article was created with
\texttt{R} packages \texttt{rticles}, \texttt{knitr}, and
\texttt{rmarkdown}. The project's GitHub repository
(\url{https://github.com/JayaniLakshika/paper-nldr-vis-algorithm})
contains all materials required to reproduce this article.

>>>>

These \texttt{R} packages were used for the work: \texttt{tidyverse}
(\citet{hadley2019}), \texttt{png} (\citet{simon2022}), \texttt{Rtsne}
(\citet{jesse2015}), \texttt{umap} (\citet{tomasz2023}),
\texttt{ggplot2} (\citet{hadley2016}), \texttt{patchwork}
(\citet{thomas2024}), \texttt{colorspace} (\citet{achim2020}),
\texttt{langevitour} (\citet{harisson2024}), \texttt{conflicted}
(\citet{hadley2023}), \texttt{reticulate} (\citet{kevin2024}),
\texttt{kableExtra} (\citet{hao2024}). These \texttt{python} packages
were used for the work:. The article was created with \texttt{R}
packages \texttt{rticles} (\citet{jjallaire2024}), \texttt{knitr}
(\citet{yihui2014}), and \texttt{rmarkdown} (\citet{yihui2020}). The
project's GitHub repository
(\url{https://github.com/JayaniLakshika/paper-nldr-vis-algorithm})
contains all materials required to reproduce this article.
